Incentivizing Exploration with Unbiased History

### 2018-10-28 llevel-overview.tex
minor change

\section{$L$-level Recommendation Policy}
\label{sec:llevel}
In this section, we give an overview of how we extend our 3-level policy to an $L$-level policy for $L > 3$ to achieve better regret. Detailed proofs and discussions can be found in Section \ref{sec:llevel-details}.

\begin{theorem}
\label{thm:llevel}
The $L$-level recommendation policy gets expected regret $O\left(T^{2^{L-1}/(2^L-1)} \log^2(T) \right)$ for $L \leq \log(\ln(T)/\log(S^4))$. In particular, if we pick $L = \log(\ln(T)/\log(S^4))$, the expected regret is $O(T^{1/2} polylog(T))$. 
\end{theorem}

\begin{corollary}
\label{cor:llevel}
With the proper setting of $L$ and $T_1,...,T_L$ described above, the $L$-level recommendation policy gets expected regret $O(\min(1/\Delta, T^{1/2})polylog(T))$. Here $\Delta = |\mu_1 -\mu_2|$ and the $L$-level recommendation policy does not need to know $\Delta$. Moreover, agent $t$ observes a subhistory of size at least $\Omega( \lfloor t/polylog(T)\rfloor)$. 
\end{corollary}

>>>>

\section{$L$-level Recommendation Policy}
\label{sec:llevel}
In this section, we give an overview of how we extend our 3-level policy to an $L$-level policy for $L > 3$ which achieves better regret. Detailed proofs and discussions can be found in Section \ref{sec:llevel-details}.

\jmcomment{Will change these statements a bit.}
\begin{theorem}
\label{thm:llevel}
The $L$-level recommendation policy gets expected regret $O\left(T^{2^{L-1}/(2^L-1)} \log^2(T) \right)$ for $L \leq \log(\ln(T)/\log(S^4))$. In particular, if we pick $L = \log(\ln(T)/\log(S^4))$, the expected regret is $O(T^{1/2} polylog(T))$. 
\end{theorem}

\begin{corollary}
\label{cor:llevel}
With the proper setting of $L$ and $T_1,...,T_L$ described above, the $L$-level recommendation policy gets expected regret $O(\min(1/\Delta, T^{1/2})polylog(T))$. Here $\Delta$ is the difference between the largest mean and second largest mean of arms and the $L$-level recommendation policy does not need to know $\Delta$. Moreover, agent $t$ observes a subhistory of size at least $\Omega( \lfloor t/polylog(T)\rfloor)$. 
\end{corollary}

Now we give some overview of the additional techniques we use for our $L$-level policy.

\xhdr{New connecting structures between levels.}

\xhdr{Additional groups for boundary cases.}
